Presentation Title

### 2017-08-15 paper/s6-conclusion.tex
Edit paper

In this work we introduced an application neutral blockchain system which we call \textsc{Checo}.
We add checkpoint block to the existing TrustChain data structure for use in our consensus protocol.
The round based consensus protocol uses ACS as a building block to reach consensus on checkpoint blocks.
The consensus result, which is a set of checkpoint blocks, lets nodes elect new facilitators and create new checkpoint blocks.
To make transactions, nodes use the transaction protocol,
which is adapted from an existing work called True Halves.
Finally, we introduce a validation protocol which ensures that if agreed fragments for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of the validation protocol is that it uses point-to-point communication,
i.e. nodes only validate the transactions of interest,
this enables our horizontal scalability property.

We achieve the properties described in the Problem Description (\Cref{sec:description}).
Namely, our protocol achieves agreement and validity as we argued in~\Cref{sec:correctness-of-validity}.
Further, the horizontal scalability is demonstrated in~\Cref{sec:implementation},
in the ideal case as well as the worst case.

>>>>

We introduced an application neutral blockchain system which we call \textsc{Checo}.
The checkpoint block is added to the existing TrustChain data structure for use in our consensus protocol.
The round based consensus protocol uses ACS as a building block to reach consensus on checkpoint blocks.
The consensus result lets nodes elect new facilitators and create new checkpoint blocks.
To make transactions, nodes use the transaction protocol,
which is adapted from an existing work called True Halves.
Finally, we introduce a validation protocol which ensures that if an agreed fragment for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of the validation protocol is that it uses point-to-point communication,
i.e. nodes only validate the transactions of interest,
this enables our horizontal scalability property.

We achieve the properties described in the Problem Description (\Cref{sec:description}).
Namely, our protocol achieves agreement and validity as we argued in~\Cref{sec:correctness-of-validity}.
Further, the horizontal scalability is demonstrated in~\Cref{sec:implementation},
in the ideal case as well as the worst case.
In the future, we hope to apply our system to a concrete application and evaluate its performance.
